### 2016-07-12 Projects/DelCo_2012/Report/DelCo_2012.tex
editorial to build
Remove Fire Suppression Graphics
Also added tests to Spray Density Appendix

To better visualize the data presented in Table~\ref{tab:Test_Results}, Fig.~\ref{fig:fs_1_1} shows the thermocouple temperature and heat flux changes for CAF Test 1 as a result of the hallway (first) and room (second) suppression actions. Fig.~\ref{fig:fs_1_2} shows the same impacts as Fig.~\ref{fig:fs_1_1}, except that the tests used water.

\begin{figure}[ht!]
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
	\label{fig:fs_1_1}
\end{figure}

\begin{figure}[ht!]
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 1 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
	\label{fig:fs_1_2}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB1} &
\includegraphics[width=3.2in]{../Figures/Bars/BB2} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB3} &
\includegraphics[width=3.2in]{../Figures/Bars/BB4}
\end{tabular*}
\caption{Spray density figures for burn building tests 1 (upper left), 2 (upper right), 3 (lower left), and 4 (lower right).}
\label{fig:bb_1_4}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB5} &
\includegraphics[width=3.2in]{../Figures/Bars/BB6} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB7} &
\includegraphics[width=3.2in]{../Figures/Bars/BB8}
\end{tabular*}
\caption{Spray density figures for burn building tests 5 (upper left), 6 (upper right), 7 (lower left), and 8 (lower right).}
\label{fig:bb_5_8}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB9} &
\includegraphics[width=3.2in]{../Figures/Bars/BB10} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB11} &
\includegraphics[width=3.2in]{../Figures/Bars/BB12}
\end{tabular*}
\caption{Spray density figures for burn building tests 9 (upper left), 10 (upper right), 11 (lower left), and 12 (lower right).}
\label{fig:bb_9_12}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB13} &
\includegraphics[width=3.2in]{../Figures/Bars/BB14} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB15} &
\includegraphics[width=3.2in]{../Figures/Bars/BB16}
\end{tabular*}
\caption{Spray density figures for burn building tests 13 (upper left), 14 (upper right), 15 (lower left), and 16 (lower right).}
\label{fig:bb_13_16}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB17} &
\includegraphics[width=3.2in]{../Figures/Bars/BB18} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB19} &
\includegraphics[width=3.2in]{../Figures/Bars/BB20}
\end{tabular*}
\caption{Spray density figures for burn building tests 17 (upper left), 18 (upper right), 19 (lower left), and 20 (lower right).}
\label{fig:bb_19_21}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=3.2in]{../Figures/Bars/BB21}
\caption{Spray density figures for burn building test 21.}
\label{fig:bb_21}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/ES_1} &
\includegraphics[width=3.2in]{../Figures/Bars/ES_2} \\
\includegraphics[width=3.2in]{../Figures/Bars/ES_3} &
\includegraphics[width=3.2in]{../Figures/Bars/ES_4}
\end{tabular*}
\caption{Spray density figures for experimental structure tests 1 (upper left), 2 (upper right), 3 (lower left), and 4 (lower right).}
\label{fig:es_1_4}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/ES_5} &
\includegraphics[width=3.2in]{../Figures/Bars/ES_6} \\
\includegraphics[width=3.2in]{../Figures/Bars/ES_7} &
\includegraphics[width=3.2in]{../Figures/Bars/ES_72}
\end{tabular*}
\caption{Spray density figures for experimental structure tests 5 (upper left), 6 (upper right), 7 (lower left), and 7.2 (lower right).}
\label{fig:es_5_72}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/ES_8} &
\includegraphics[width=3.2in]{../Figures/Bars/ES_9} \\
\includegraphics[width=3.2in]{../Figures/Bars/ES_10} &
\includegraphics[width=3.2in]{../Figures/Bars/ES_11}
\end{tabular*}
\caption{Spray density figures for experimental structure tests 8 (upper left), 9 (upper right), 10 (lower left), and 11 (lower right).}
\label{fig:es_8_11}
\end{figure}

@@

\chapter{Fire Suppression Figures}
\label{app:fire_suppression}

\begin{figure}[ht!]
\includegraphics[width=.82\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
\includegraphics[width=.82\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_1}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 1 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_2}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest3FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest3SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 2 with a 7/8'' 
Solid Stream nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_3}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest4FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest4SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 2 with a 7/8'' 
Solid Stream nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_4}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest5FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest5SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 3 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_5}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest6FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest6SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 3 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_6}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest7FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest7SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 4 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_7}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest8FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest8SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 4 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_8}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest11FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest11SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 5 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_11}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest12FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest12SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 5 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_12}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest13FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest13SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 6 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_13}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest14FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest14SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 6 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_14}
\end{figure}

>>>>

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB1} &
\includegraphics[width=3.2in]{../Figures/Bars/BB2} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB3} &
\includegraphics[width=3.2in]{../Figures/Bars/BB4}
\end{tabular*}
\caption{Spray density figures for burn building tests 1) Water Straight Stream Back (upper left), 2) Water Straight Stream Back (upper right), 3) Water Straight Stream Mid (lower left), and 4) Water Straight Stream Mid (lower right).}
\label{fig:bb_1_4}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB5} &
\includegraphics[width=3.2in]{../Figures/Bars/BB6} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB7} &
\includegraphics[width=3.2in]{../Figures/Bars/BB8}
\end{tabular*}
\caption{Spray density figures for burn building tests 5) Water Straight Stream Mid (upper left), 6) Water Fog Mid (upper right), 7) Water Fog Mid (lower left), and 8) Water Fog Back (lower right).}
\label{fig:bb_5_8}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB9} &
\includegraphics[width=3.2in]{../Figures/Bars/BB10} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB11} &
\includegraphics[width=3.2in]{../Figures/Bars/BB12}
\end{tabular*}
\caption{Spray density figures for burn building tests 9) Water Fog Back (upper left), 10) Water Solid Stream Back (upper right), 11) Water Solid Stream Back (lower left), and 12) CAF Solid Stream Back (lower right).}
\label{fig:bb_9_12}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB13} &
\includegraphics[width=3.2in]{../Figures/Bars/BB14} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB15} &
\includegraphics[width=3.2in]{../Figures/Bars/BB16}
\end{tabular*}
\caption{Spray density figures for burn building tests 13) CAF Solid Stream Mid (upper left), 14) CAF Solid Stream Back (upper right), 15) CAF Solid Stream Mid (lower left), and 16) CAF Fog Mid (lower right).}
\label{fig:bb_13_16}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB17} &
\includegraphics[width=3.2in]{../Figures/Bars/BB18} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB19} &
\includegraphics[width=3.2in]{../Figures/Bars/BB20}
\end{tabular*}
\caption{Spray density figures for burn building tests 17) CAF Straight Stream Mid (upper left), 18) CAF Straight Stream Mid (upper right), 19) CAF Fog Back (lower left), and 20) CAF Fog Back (lower right).}
\label{fig:bb_19_21}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=3.2in]{../Figures/Bars/BB21}
\caption{Spray density figures for burn building test 21) CAF Straight Stream Back.}
\label{fig:bb_21}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/ES_1} &
\includegraphics[width=3.2in]{../Figures/Bars/ES_2} \\
\includegraphics[width=3.2in]{../Figures/Bars/ES_3} &
\includegraphics[width=3.2in]{../Figures/Bars/ES_4}
\end{tabular*}
\caption{Spray density figures for experimental structure tests 1) Water Straight Stream FR (upper left), 2) Water Straight Stream FR (upper right), 3) Water Straight Stream FR (lower left), and 4) Water Straight Stream FR (lower right).}
\label{fig:es_1_4}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/ES_5} &
\includegraphics[width=3.2in]{../Figures/Bars/ES_6} \\
\includegraphics[width=3.2in]{../Figures/Bars/ES_7} &
\includegraphics[width=3.2in]{../Figures/Bars/ES_72}
\end{tabular*}
\caption{Spray density figures for experimental structure tests 5) Water Fog FR (upper left), 6) Water Fog FR (upper right), 7) Water Solid Stream FR (lower left), and 8) Water Solid Stream H (lower right).}
\label{fig:es_5_72}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/ES_8} &
\includegraphics[width=3.2in]{../Figures/Bars/ES_9} \\
\includegraphics[width=3.2in]{../Figures/Bars/ES_10} &
\includegraphics[width=3.2in]{../Figures/Bars/ES_11}
\end{tabular*}
\caption{Spray density figures for experimental structure tests 9) Water Fog H (upper left), 10) Water Fog H (upper right), 11) Water Straight Stream H (lower left), and 12) Water Straight Stream H (lower right).}
\label{fig:es_8_11}
\end{figure}

@@

\chapter{Fire Suppression Data}
\label{app:fire_suppression}
